Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] fixed typo.
Cosmetic changes.

With the derivation rules we produce derivation trees inside
the judgments. These trees represent proofs of theorems.
We use such level of expressiveness for the reconstructed proofs
from the \ATPs.

@@

This paper adopts the notion of \emph{structurally smaller} from
\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
structurally recursive if it calls itself with only
structurally smaller arguments.

@@

Following the technique mentioned above, we get the structural
recursive definition of the $\fuh_{0}$ function presented
in~\eqref{eq:uh}.

\begin{align}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
  \end{split}
\end{align}

@@

For a more complete treatment of general recursion, and how to
define well-founded and well-structural recursive functions, we refer
the reader to \citeauthor{Bove2005}~\cite{Bove2005}.

>>>>

With the derivation rules we produce derivation trees inside
the judgments. These trees represent proofs of theorems.
We use such level of expressiveness for the reconstructed proofs
of the \ATPs.

@@

This paper adopts the notion of \emph{structurally smaller}
from~\cite{Abel2002}, that is, a recursive function is structurally
recursive if it calls itself with only structurally smaller arguments.

@@

Following the technique mentioned above, we define the
function~$\fuh$, the structural
recursive definition of the function~$\fuh_{0}$.
\begin{align*}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
  \end{split}
\end{align*}

@@

For a more complete treatment of general recursion, and how to define
well-founded and well-structural recursive functions, we refer the
reader to~\cite{Bove2005}.
